---
weight: 1
title: "Chapter 6"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::knit_hooks$set(class = function(before, options, envir) {
  if(before) {
    sprintf("<div class = '%s'>", options$class)
  } else {
    "</div>"
  }
})
```

## 6.1 Risk and Risk Aversion
$$ U = E(R) - \frac{1}{2} A \sigma^2 $$

* Risk Averse
  + $A < 0$

* Risk-Neutral
  + $A = 0$

* Risk Lover
  + $A > 0$

{{% notice tip %}}
**Mean-Variance (M-V) criterion** Portfolio `$A$` dominates portfolio $B$ if $E(r_A) >= E(r_B)$ and $\\sigma_A <= \sigma_B$, with one of the inequalities being strict.
{{% /notice %}}

{{% notice tip %}}
**Indifference Curve** Curve in the mean-variance plane connecting all portfolio points with equal utility.
{{% /notice %}}

```{r indifference-curve, fig.cap = "Indifference curve", fig.width = 5, fig.height = 5, echo=FALSE, warning=FALSE}
library(ggplot2)
library(magrittr)
library(fbhelpers)
library(latex2exp)

x <- -100:100
f <- function(x) x^2
dat <- data.frame(x,y=f(x))
dat %>% 
  ggplot(aes(x,y)) + 
  stat_function(fun = f, colour="blue", size = 1,
                xlim = c(0, 10)) +
  theme_emblem() + 
  geom_vline(xintercept = 5, linetype = "AA") +
  geom_hline(yintercept = f(5), linetype = "AA") +
  scale_x_continuous(breaks = c(5), 
                     limits  = c(1,9),
                     labels = TeX("$\\sigma_p$"),
  ) +
  scale_y_continuous(breaks = c(f(5)), 
                     limits = c(0,100),
                     labels = TeX("$E(r_P)$"),
  ) +
  
  ggtitle(TeX("$E(r)$")) + 
  
  geom_point(x = 5, y = f(5), size = 2) + 
  annotate("text", x = 5 + 0.25, y = f(5) - 2, label = "P") +
  
  geom_point(x = 7, y = f(7), size = 2) + 
  annotate("text", x = 7 + 0.25, y = f(7), label = "Q") +
  
  theme(plot.title = element_text(hjust = 0),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text = element_text(size = 12),
        title = element_text(size = 15)) + 
  
  theme(plot.background = element_rect(fill = "white")) +
  
  annotate("segment", 
           x = 8, 
           y = f(6), 
           xend = 6, 
           yend = f(6),
           arrow = arrow(angle = 20, length = unit(2, "mm"), type = "closed")) + 
  annotate("label", x = 8, y = f(6), label = "Indifference\nCurve",
           color = "black")

```



## 6.2 Capital Allocation Across Risky and Risk-Free Portfolios

{{% notice tip %}}
**Complete Portfolio** The portfolio consisting of one's risk-free and *and* risky assets.
{{% /notice %}}

## 6.3 The Risk Free Asset

## 6.4 Portfolios of One Risky Asset and a Risk-Free Asset

{{% notice warning %}}
Nongovernmental investors cannot borrow at the risk-free rate.  Therefore, in the borrowing range of the CAL, the risk-free $r_f$ rate becomes the borrowing rate $r_B > r_f$ and as a result the CAL will be kinked.
{{% /notice %}}
## 6.5 Risk Tolerance and Asset Allocation

It is natural to ask what allocation(s) maximize utility.

$$ \begin{align} \mathop{argmax}_y (U) &= E(r_C) - \frac{1}{2} A \sigma^2_C \\
&= r_f + y[E(r_P) - r_f] - \frac{1}{2} A y^2 \sigma^2_P  \end{align}$$

We proceed by taking the derivative of both sides with respect to $y$.  

$$ \begin{align} 0 &= E(r_P) - r_f - Ay^*\sigma^2_P \\ \implies y^* &= \frac{E(r_P) - r_f}{A\sigma^2_P}   \end{align} $$

Note that the risky allocation percentage is:

* directly proportional to the risk premium of the risky asset
* inversely proportional to the risk aversion of the investor
* inversely proportional to the variance of the risky asset

#### Example

Suppose the risk aversion of an investor is 4, the risk-free rate is 7%, the expected
return of the risky asset is 15% with standard deviation 22%.  What is the optimal
percent investment in the risky-asset for this investor?

$$y^* = \frac{0.15 - 0.07}{4 * 0.22^2} = `r scales::percent((0.15 - 0.07)/(4 * 0.22^2),1, suffix ='\\%')` $$

With this optimal allocation, the return on the complete portfolio will be $E(r_C) = 0.07 + 0.41 \cdot (0.15 - 0.07) = 10.28\% $  The standard deviation will be $\sigma_C = 0.41 * 0.22 = 9.02\% $.

## 6.6 Passive Strategies: The Capital Market Line



* Risk premium
+ Definition

* Fair Game
+ Definition

* Utility
+ Definition

* Certainty Equivalent Rate
+ Definition

* Risk Neutral
+ Definition


{{% notice definition %}}
test 
{{% /notice %}}
