---
weight: 1
title: "Chapter 6"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 6.1 Risk and Risk Aversion

```{r}
library(ggplot2)
library(magrittr)
library(fbhelpers)
library(latex2exp)

x <- -100:100
dat <- data.frame(x,y=3x^2)
f <- function(x) 3*x^2
dat %>% 
  ggplot(aes(x,y)) + 
    #geom_point()+
    stat_function(fun = f, colour="blue", size = 1,
                  xlim = c(25, 35)) +
  theme_emblem() + 
  geom_vline(xintercept = 30, linetype = "AA") +
  geom_hline(yintercept = f(30), linetype = "AA") +
  scale_x_continuous(breaks = c(30), 
                     limits  = c(20,40),
                     labels = TeX("$\\sigma_p$"),
                     #expand = c(0.3,0.3)
                     ) +
  scale_y_continuous(breaks = c(f(30)), 
                     labels = TeX("$E(r_P)$"),
                     #expand = c(0.3, 0.3)
                     ) +
  ggtitle(TeX("$E(r)$")) + 
  geom_point(x = 30, y = f(30), size = 2) + 
  theme(plot.title = element_text(hjust = 0),
        axis.title.y = element_blank(),
        axis.title.x = element_blank()) + 
   annotate("text", x = 39, y = f(35), label = "Indifference\nCurve") +
    annotate("segment", 
             x = 37, 
             y = f(35), 
             xend = 35, 
             yend = f(35),
             arrow = arrow(angle = 20, length = unit(2, "mm"), type = "closed"))
  
```

## 6.2 Capital Allocation Across Risky and Risk-Free Portfolios

## 6.3 The Risk Free Asset

## 6.4 Portfolios of One Risky Asset and a Risk-Free Asset

## 6.5 Risk Tolerance and Asset Allocation

## 6.6 Passive Strategies: The Capital Market Line



* Risk premium
  + Definition
  
* Fair Game
  + Definition
  
* Utility
  + Definition
  
* Certainty Equivalent Rate
  + Definition
  
* Risk Neutral
  + Definition

$$ U = E(R) - \frac{1}{2} A \sigma^2 $$

{{% notice definition %}}
 test 
{{% /notice %}}
